Incentivizing Exploration with Unbiased History

### 2018-11-02 main.tex
final

% a very useful package for edits and comments, from David Kempe (USC)
\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}      % as for Alex
\addauthor{jm}{blue}     % jm for Jieming
\addauthor{ni}{magenta}     % ni for Nicole
\addauthor{sw}{brown}     % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

@@

\author{
Nicole Immorlica
\and
Jieming Mao
\and
Aleksandrs Slivkins
\and
Zhiwei Steven Wu
}
\begin{document}
\begin{titlepage}
\maketitle

>>>>

% a very useful package for edits and comments, from David Kempe (USC)
%\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
%\addauthor{as}{red}      % as for Alex
%\addauthor{jm}{blue}     % jm for Jieming
%\addauthor{ni}{magenta}     % ni for Nicole
%\addauthor{sw}{brown}     % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

@@

\author{
Nicole Immorlica \thanks{Microsoft Research, email: nicimm@microsoft	.com.}
\and
Jieming Mao \thanks{University of Pennsylvania, email: maojm517@gmail.com.}
\and
Aleksandrs Slivkins  \thanks{Microsoft Research, email: slivkins@microsoft.com.}
\and
Zhiwei Steven Wu  \thanks{University of Minnesota, email: zsw@umn.edu.}
}
\begin{document}
\begin{titlepage}
\maketitle

### 2018-11-02 model.tex
final

\xhdr{Preliminaries.}
\asedit{We assume that $K$ is constant, and focus on the dependence on $T$. However, we explicitly state the dependence on $K$, \eg using the $O_K()$ notation.}

@@

\asedit{We use the notion of \emph{reward tape} to simplify the application of (anti-)concentration inequalities. This is a $K\times T$ random matrix with rows and columns corresponding to arms and rounds, respectively. For each arm $a$ and round $t$, the value in cell $(a,t)$ is drawn independently from Bernoulli distribution $\mD_a$. W.l.o.g., rewards in our model are defined by the rewards tape: namely, the reward for the $j$-th pull of arm $a$ is taken from the $(a,j)$-th entry of the reward matrix.}

>>>>

\xhdr{Preliminaries.}
We assume that $K$ is constant, and focus on the dependence on $T$. However, we explicitly state the dependence on $K$, \eg using the $O_K()$ notation.

@@

We use the notion of \emph{reward tape} to simplify the application of (anti-)concentration inequalities. This is a $K\times T$ random matrix with rows and columns corresponding to arms and rounds, respectively. For each arm $a$ and round $t$, the value in cell $(a,t)$ is drawn independently from Bernoulli distribution $\mD_a$. W.l.o.g., rewards in our model are defined by the rewards tape: namely, the reward for the $j$-th pull of arm $a$ is taken from the $(a,j)$-th entry of the reward matrix.
